Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-12-09 paper/manuscript.tex
Add NES in Orion to software section

    \item \href{https://www.cresset-group.com/software/flare/}{Flare} is a commercial structure-based drug design software offered by Cresset. Similar to FEP+ it has an easily accessible graphical user interface and strives to facilitate free energy calculations for non-experts while offering advanced users full control via a Python API. It only runs on GPUs, using CUDA or OpenCL~\cite{kuhn2020assessment}. It is build on top of the open source software packages Sire and BioSimSpace (cf. below).

>>>>

    \item \href{https://www.cresset-group.com/software/flare/}{Flare} is a commercial structure-based drug design software offered by Cresset. Similar to FEP+ it has an easily accessible graphical user interface and strives to facilitate free energy calculations for non-experts while offering advanced users full control via a Python API. It only runs on GPUs, using CUDA or OpenCL~\cite{kuhn2020assessment}. It is built on top of the open source software packages Sire and BioSimSpace (cf. below).
    \item \href{https://www.eyesopen.com/orion}{Orion}, OpenEye's cloud platform, offers relative binding free energy calculations using non-equilibrium switching (Section~\ref{sec:sampling_schemes})~\cite{sorensen2024orion}.
